Meta-analysis fear learning

### 2022-02-21 manuscript/manuscript.Rmd
update 2022-02-21 19:22:02

```{r setup, include=FALSE}
run_everything = TRUE
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

To examine the effect of a categorical variable,
a reference category must be chosen.
Dummy variables encode the difference between each remaining category and this reference category.
When examining the results,
the intercept represents the expected effect size for a study that falls within the reference category for all categorical variables.
The effect of dummy variables represents the difference of that category with the reference category.
If a dummy variable has a significant effect, that means that that group's mean differs significantly from the reference category's mean (i.e., from the intercept).

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  catvars <- sapply(df, class) == "factor" & names(df) %in% mods
  df[catvars] <- lapply(df[catvars], function(v){
    tab <- table(v)
    relevel(v, ref = names(tab)[which.max(tab)])
  })
  refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  names(refcat) <- c("Variable", "Reference")
  modmat <- model.matrix(~., df[mods])
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

>>>>

```{r setup, include=FALSE}
run_everything = FALSE
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

To examine the effect of a categorical variable,
we used deviation coding.
This means that the intercept represents the grand mean accross all categories of the categorical variables.
Dummy variables encode the difference between each category and this grand mean.
To ensure model identification, one category is not compared to the grand mean.
This was always the smallest category in the analyses below.

When examining the results,
the intercept represents the overall effect size for the entire sample.
The effect of dummy variables represents the difference of that category with the overall effect size.
If a dummy variable has a significant effect, that means that that group's mean differs significantly from the grand mean (i.e., from the intercept).

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  catvars <- sapply(df, class) == "factor" & names(df) %in% mods
  df[catvars] <- lapply(names(df)[catvars], function(n){
    v <- droplevels(df[[n]])
    tab <- table(v)
    if(length(tab) == 1) return(v)
    v <- relevel(v, ref = names(tab)[which.min(tab)])
    conts <- try(contr.sum(length(levels(v))))
    if(inherits(conts, "try-error")) return(v)
    conts <- conts[nrow(conts):1, , drop = FALSE]
    colnames(conts) <- paste0("Mvs", levels(v)[apply(conts, 2, function(x){ which(x == 1) })])
    tryCatch({contrasts(v) <- conts}, error = function(e){
      browser()
    })
    return(v)
  })

  refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  names(refcat) <- c("Variable", "Reference")
  mods <- mods[sapply(df[mods], function(x){length(unique(x)) > 1})]
  modmat <- model.matrix(~., df[mods])
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

### 2022-02-21 manuscript/tab_rma_template.Rmd
update 2022-02-21 19:22:02

>>>>

```{r tabref{{i}}, results = 'asis'}
p <- processes[{{i}}]
    tb <- modres[[{{i}}]]$refcat
    # knitr::kable(tb, caption = paste0("Reference category for each variable for process ", p))
    datatable(
          tb,
          rownames = FALSE,
          caption = paste0("Category not compared to the grand mean for each variable for process ", p))
```
